SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-11 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Add more explanation on page 5.

\renewcommand{\P}{\mathcal V}
\def\Talg{\mathcal{T}_{\Sigma,\P}}
Formally, we assume the existence of a term algebra $\Talg$,
where $\Sigma$ is the signature of the data and action constructors,
and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
data expressions $\mathcal{E}_\P$, including a set of Boolean
expressions $\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
On top of $\mathcal{E}_\P$ we build the action algebra
$\mathcal{A}_\P$, with $\mathcal{A}_\P\subseteq\mathcal{T}_\P \wedge
\mathcal{E}_\P\cap\mathcal{A}_\P=\emptyset$;
 action terms will use data expressions as sub-terms.
The function $\vars(t)$ identifies the set of variables in a term
$t\in\AlgT$.

@@

  \ERIC{
The PLTS of the controller $CState$ from Example \ref{example:EnableOperator} is  $\langle S,s_0, \to\rangle$, where:
$$S=\{0, 1\}; s_0=0;
	 \to=\{0\xrightarrow{l}0, 0\xrightarrow{\delta}1, 1\xrightarrow{r}1\}$$.
}
  \QIN{
%Featuring guards and assignments in the label of transitions, 
\YX{And the PLTS of the controller $CData$ is $\langle S',s'_0, \to\rangle$} where:
 \ERIC{$$S'=\{0\}; s'_0=0; vars(0)=\{v\}; \texttt{init}\ \{v:=0\};$$
	 $$\to=\{0\xrightarrow{l, [v=0]}0, 0\xrightarrow{\delta,  [v=0], \{v:=1\}}0, 0\xrightarrow{r, [v=1]}0\}$$.
  }}
\ERIC{The PLTSs contained in $EnableStateCompLeft$ are similar to the PLTS $CState$, but their action constants have been renamed, ensuring disjoint state variable sets.}
\end{example}

@@

\vspace{-5mm}
\begin{figure}[ht]
\centerline{ 
  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable1-aut}
  \hspace{25mm}
  \includegraphics[width=0.20\linewidth]{ActaXFIG/Enable2-aut}}
  \begin{minipage}{5.7cm}
$  \begin{array}{@{}r@{}l@{}}
    ot_1  = &\openrule{\{ \xrightarrow{a_1}_P \},\\ [\forall y_1. a_1\neq\delta(y_1)]}
    {A_0 \xrightarrow{a_1} A_0}\\
    ot_2  =& \openrule{
                            \{\xrightarrow{\delta(x_1)}_P,\,
                            \xrightarrow{acc(x_1)}_Q\}  }
    {A_0 \xrightarrow{\underline{\delta(x_1)}} A_1}\\
    ot_3  =& \openrule{
                          \{  \xrightarrow{a_2}_Q \},\\ [\forall y_2. a_2\neq acc(y_2)] }
    {A_1 \xrightarrow{a_2} A_1}
  \end{array}$
  \end{minipage}
  \hspace{2mm}
  \begin{minipage}{6cm}
$  \begin{array}{@{}r@{}l@{}}
    ot'_1  =& \openrule{
    	\{\xrightarrow{b_1}_P\}, ~~ [\forall y_1. b_1\neq\delta(y_1) \!\land\! v=0]}
    {B_0 \xrightarrow{b_1} B_0}\\
    ot'_2  =& \openrule{
                            \{\xrightarrow{\delta(y_2)}_P,\,
                            \xrightarrow{acc(x_2)}_Q \},~
                                        v=0,~
                                        \{v\gets 1\}}
    {B_0 \xrightarrow{\underline{\delta(x_2)}} B_1}\\
    ot'_3  =& \openrule{
                            \{\xrightarrow{b_2}_Q\}, ~~ [\forall y_2. b_2\neq acc(y_2) \!\land\! v=1] }
    {B_1 \xrightarrow{b_2} B_1}
  \end{array}$
  \end{minipage}
  \caption{The two open automata}
  \label{schema:enable-OAs}
\end{figure}

>>>>

\renewcommand{\P}{\mathcal V}
\def\Talg{\mathcal{T}_{\Sigma,\P}}
Formally, we assume the existence of a term algebra $\Talg$,
where $\Sigma$ is the signature of the data and action constructors,
and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
data expressions $\mathcal{E}_\P$, including a set of Boolean
expressions $\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
On top of $\mathcal{E}_\P$ we build the action algebra
$\mathcal{A}_\P$, with $\mathcal{A}_\P\subseteq\mathcal{T}_\P$.
\QIN{As action expressions $\mathcal{A}_\P$ we built will not be used to present data terms, we have} 
$\mathcal{E}_\P\cap\mathcal{A}_\P=\emptyset$;
 action terms will use data expressions as sub-terms.
The function $\vars(t)$ identifies the set of variables in a term
$t\in\AlgT$.

@@

  \ERIC{
The PLTS of the controller $CState$ from Example \ref{example:EnableOperator} is  $\langle S,s_0, \to\rangle$, where:
$$S=\{0, 1\}; s_0=0;
	 \to=\{0\xrightarrow{l}0, 0\xrightarrow{\delta}1, 1\xrightarrow{r}1\}.$$
}
  \QIN{
%Featuring guards and assignments in the label of transitions, 
\YX{And the PLTS of the controller $CData$ is $\langle S',s'_0, \to\rangle$} where:
 \ERIC{$$S'=\{0\}; s'_0=0; vars(0)=\{v\}; \texttt{init}\ \{v:=0\};$$
	 $$\to=\{0\xrightarrow{l, [v=0]}0, 0\xrightarrow{\delta,  [v=0], \{v:=1\}}0, 0\xrightarrow{r, [v=1]}0\}.$$
  }}
\ERIC{The PLTSs contained in $EnableStateCompLeft$ are similar to the PLTS $CState$, but their action constants have been renamed, ensuring disjoint state variable sets.}
\end{example}

@@

\vspace{-5mm}
\begin{figure}[ht]
\centerline{ 
  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable1-aut}
  \hspace{25mm}
  \includegraphics[width=0.20\linewidth]{ActaXFIG/Enable2-aut}}
  \begin{minipage}{5.7cm}
$  \begin{array}{@{}r@{}l@{}}
    ot_1  = &\openrule{\{ \xrightarrow{a_1}_P \},\\ [\forall y_1. a_1\neq\delta(y_1)]}
    {A_0 \xrightarrow{a_1} A_0}\\
    ot_2  =& \openrule{
                            \{\xrightarrow{\delta(x_1)}_P,\,
                            \xrightarrow{acc(x_1)}_Q\}  }
    {A_0 \xrightarrow{\underline{\delta(x_1)}} A_1}\\
    ot_3  =& \openrule{
                          \{  \xrightarrow{a_2}_Q \},\\ [\forall y_2. a_2\neq acc(y_2)] }
    {A_1 \xrightarrow{a_2} A_1}
  \end{array}$
  \end{minipage}
  \hspace{2mm}
  \begin{minipage}{6cm}
$  \begin{array}{@{}r@{}l@{}}
    ot'_1  =& \openrule{
    	\{\xrightarrow{b_1}_P\}, ~~ [\forall y_1. b_1\neq\delta(y_1) \!\land\! v=0]}
    {B_0 \xrightarrow{b_1} B_0}\\
    ot'_2  =& \openrule{
                            \{\xrightarrow{\delta(x_2)}_P,\,
                            \xrightarrow{acc(x_2)}_Q \},~
                                        v=0,~
                                        \{v\gets 1\}}
    {B_0 \xrightarrow{\underline{\delta(x_2)}} B_1}\\
    ot'_3  =& \openrule{
                            \{\xrightarrow{b_2}_Q\}, ~~ [\forall y_2. b_2\neq acc(y_2) \!\land\! v=1] }
    {B_1 \xrightarrow{b_2} B_1}
  \end{array}$
  \end{minipage}
  \caption{The two open automata}
  \label{schema:enable-OAs}
\end{figure}
